---
flexdashboard::flex_dashboard:
runtime: shiny
---
  
```{r tmapping-123, message=FALSE}
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(mapview) # for interactive maps
library(ggplot2) # tidyverse data visualization package
library(shiny)   # for web applications
library(spData)
library(dplyr)
library(sf)
library(bookdown)
library(leaflet)
library(leaflet.extras)
library(geojsonio)
library(sf)
library(raster)
library(dplyr)
library(spData)
library(kableExtra)
# library(spDataLarge)
```

# Adding additional information {#contentadd}

Using and applying GIS techniques in R has become much easier since the additional functionality of Java-script libraries. One of these libraries in the `leaflet` library for mapping. Below are some examples of these mapping tools with examples.

I like the idea of know what to do in arcGIS so that it is easy to work with researchers that use either R or arcGIS. For a GIS map there are two main options. Here are the resources for building interactive and static maps in R using a range of different packages:

- `leaflet`
- `tmap`

### Adding points

THere are quite a few datasets to combine here but the key aspect here is that we can do all of this semlessly with the data in a `tidy` format.

The datasets we are going to merge here are:

- `nz`
- `kml data`
- `abunance data`

#### Point locations (`nz + kml data`)

```{r}
source("./R/kml_to_tidy.R")
kable(tidy.kat, format = "markdown")

glimpse(nz)
glimpse(tidy.kat)

m.kat <- tidy.kat %>%
            transmute(Name = folder,
                   Island = "South",
                   Land_area = NA,
                   Population = NA,
                   Sex_ratio = NA,
                   # geom = NA,
                   lat = latitude,
                   long = longitude,
                   alt = altitude)

plot.dat1 <- full_join(nz, m.kat)
glimpse(plot.dat1)

# nz %>%
#   # mutate(grid = )
```

### Plots

```{r}
library(tmap)
tm_shape(plot.dat1) + 
  tm_fill(col = "black", alpha = 0.3) +
   tm_borders(col = "blue") +
  # tm_compass(type = "8star", position = c("left", "top")) +
  tm_compass(type = "arrow", position = c("left", "top")) +
  tm_scale_bar(breaks = c(0, 100, 200), text.size = 1) +
  tm_dots(col = "black", size = 4)
?tm_dots
```

Is it easier to work with polygons and centriod points as above??

## *coming*

#### Abundance

```{r}
abund.dat5 <- read_csv("../data/abundance5.csv")
glimpse(abund.dat5)

### summarizing abundance data

# sum.dat <- abund.dat5 %>%
#               group_by()

### merge to datasets

# dat.nz.add <- nz %>% 
#                 mutate()
                
```