# Introduction {#intro}

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(spData)
library(dplyr)
library(sf)
library(bookdown)
library(leaflet) # for interactive maps
library(leaflet.extras)
library(geojsonio)
library(tmap)    # for static and interactive maps
# library(mapview) # for interactive maps
library(shiny)   # for web applications
```

*Creating maps using spatial data in R*

GIS is an area of R coding I have kept away from hoping that I would work it out at a later date. Sadly, it has got to the point where I want to be able to build more complex maps in shiny applications towards the end of my PhD and need to create a base of code to go from. Luckily, the text book "Spatial Analysis in R" has just come out in its second edition and is available in as a bookdown repository including the full text [here](https://bookdown.org/robinlovelace/geocompr/).
This page is a outline of the current resources I am working on and using for my publication and website maps. I have begun by using my normal reproducible workflow and file structure.


**EXAMPLE** You can use things like `addWMSTiles()` to add WMS (Web Map Service) tiles. The map below shows the Base Reflectivity (a measure of the intensity of precipitation occurring) using the WMS from the [Iowa Environmental Mesonet ](http://mesonet.agron.iastate.edu):

```{r fig.height=2.5}
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 4) %>%
  addWMSTiles(
    "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
    layers = "nexrad-n0r-900913",
    options = WMSTileOptions(format = "image/png", transparent = TRUE),
    attribution = "Weather data © 2012 IEM Nexrad"
  )
```

### NZ layers

```{r}
# Add fill layer to nz shape
tm_shape(nz) +
  tm_fill() 
# Add border layer to nz shape
tm_shape(nz) +
  tm_borders() 
# Add fill and border layers to nz shape
tm_shape(nz) +
  tm_fill() +
  tm_borders() 
```

#### Attributes

```{block2 qtm, type = 'rmdnote'}
`qtm()` is a handy function to create **q**uick **t**hematic **m**aps (hence the snappy name).
It is concise and provides a good default visualization in many cases:
`qtm(nz)`, for example, is equivalent to `tm_shape(nz) + tm_fill() + tm_borders()`.
Further, layers can be added concisely using multiple `qtm()` calls, such as `qtm(nz) + qtm(nz_height)`.
The disadvantage is that it makes aesthetics of individual layers harder to control, explaining why we avoid teaching it in this chapter.
```

```{r}
map_nz = tm_shape(nz) + tm_polygons()
class(map_nz)
#> [1] "tmap"
nz_water = st_union(nz) %>% st_buffer(22200) %>% 
  st_cast(to = "LINESTRING")

g = st_graticule(nz, lon = c(170, 175), lat = c(-45, -40, -35))
plot(nz_water, graticule = g, axes = TRUE, col = "blue")
# raster::plot(nz_elev / 1000, add = TRUE)
# map_nz1 = map_nz +
#   tm_shape(nz_elev) + tm_raster(alpha = 0.7)
plot(st_geometry(nz), add = TRUE)

# map_nz2 = map_nz1 +
#   tm_shape(nz_water) + tm_lines()

# map_nz3 = map_nz2 +
#   tm_shape(nz_height) + tm_dots()

# tmap_arrange(map_nz1, map_nz2, map_nz3)
```

#### Asthetics

```{r}
ma1 = tm_shape(nz) + tm_fill(col = "red")
ma2 = tm_shape(nz) + tm_fill(col = "red", alpha = 0.3)
ma3 = tm_shape(nz) + tm_borders(col = "blue")
ma4 = tm_shape(nz) + tm_borders(lwd = 3)
ma5 = tm_shape(nz) + tm_borders(lty = 2)
ma6 = tm_shape(nz) + tm_fill(col = "red", alpha = 0.3) +
  tm_borders(col = "blue", lwd = 3, lty = 2)
tmap_arrange(ma1, ma2, ma3, ma4, ma5, ma6)
```

