# Introduction {#intro}

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(spData)
library(dplyr)
library(sf)
library(bookdown)
library(leaflet)
library(leaflet.extras)
library(geojsonio)
```

*Creating maps using spatial data in R*

GIS is an area of R coding I have kept away from hoping that I would work it out at a later date. Sadly, it has got to the point where I want to be able to build more complex maps in shiny applications towards the end of my PhD and need to create a base of code to go from. Luckily, the text book "Spatial Analysis in R" has just come out in its second edition and is available in as a bookdown repository including the full text [here](https://bookdown.org/robinlovelace/geocompr/).
This page is a outline of the current resources I am working on and using for my publication and website maps. I have begun by using my normal reproducible workflow and file structure.

### WMS Tiles

You can use `addWMSTiles()` to add WMS (Web Map Service) tiles. The map below shows the Base Reflectivity (a measure of the intensity of precipitation occurring) using the WMS from the [Iowa Environmental Mesonet ](http://mesonet.agron.iastate.edu):

```{r fig.height=2.5}
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 4) %>%
  addWMSTiles(
    "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
    layers = "nexrad-n0r-900913",
    options = WMSTileOptions(format = "image/png", transparent = TRUE),
    attribution = "Weather data © 2012 IEM Nexrad"
  )
```
