# Diving In {#divingin}

```{r message=FALSE, warning=FALSE, include=FALSE}
library(spData)
library(dplyr)
library(sf)
library(bookdown)
library(leaflet)
library(leaflet.extras)
library(geojsonio)
```

There are plenty of github repositories explaining the different types of GIS and using R. Below is the public `google-my-maps` map that can be modified an worked on from within the window provided below.

## `kml` to `tidy` dataset

Import data from downloaded `kml` file from the my-maps data.

1. Download the `kml` file from online (NOT the `kmz` file)

{.:Note} A `KMZ` file is just a zipped `KML` [file](https://en.wikipedia.org/wiki/Keyhole_Markup_Language), possibly with associated embedded images, icons, etc. 

So any program that supports `KMZ` files internally unzips them to access their KML files. That may be a reason why many open source programs do not bother supporting KMZ once KML support is implemented: you just need to use an additional unzipping library of your choice, to convert the KMZ to KML. The linked posts give some JavaScript-based solutions for unzipping.

```{r}
source("./R/kml_to_tidy.R")
tidy.kat
```

### Save

Save csv data for arcGIS work from here as:

```{r}
write.csv(tidy.kat, "./data/kml_tidy_data.csv")
```


