---
title: "An Interactive Map"
subtitle: "A very simple example"
output: 
  rmarkdown::html_document: default
flexdashboard::flex_dashboard:
runtime: shiny
---
  
```{r libraries-info}
library(leaflet)
library(leaflet.extras)
```

Using and applying GIS techniques in R has become much easier since the additional functionality of Java-script libraries. One of these libraries in the `leaflet` library for mapping. Below are some examples of these mapping tools with examples.

## Resources

I like the idea of know what to do in arcGIS so that it is easy to work with researchers that use either R or arcGIS. For a GIS map there are two main options. Here are the resources for building interactive and static maps in R using a range of different packages:

- 'leaflet`

### A single location on a map

Here is the birthplace of R plotted with `leaflet`, `addTiles` and the `addMarkers`...

```{r, echo = FALSE}
# my_data <- mpd.m
p_list <- list()

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R") %>% addMyResetMapButton()
# m  
# save a ggplot

# Print the map

lm <- leaflet() %>% 
  addTiles() %>%
    setView(-93.65, 42.0285, zoom = 17) %>%
      addPopups(
    -93.65, 42.0285,
    'Here is the <b>Department of Statistics</b>, ISU') %>% addMyResetMapButton()
# lm

p_list[[1]] <- list(print(m), "Map option 1")
p_list[[2]] <- list(print(lm), "Map option 2")
```

### Leaflet plot options

*still coming*

## My Notes

I have sent the following to Matt to input into arcGIS and compare rendered maps.

```{r}
# grid.locations <- 
# label


```

*add hand drawn image here*

### Extracting mymaps data

This is for security reasons.

```{r}

```





