---
title: "An Interactive Map"
output: 
rmarkdown::html_document: default
---
  
```{r libraries-info}
library(leaflet)
```

## Map test 1

Here is the birthplace of R

```{r auckland-uni}
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m  # Print the map
```

## Map test 2

Below is a interactive map shows the location of a statistics department.

```{r leaflet-map1, out.width='50%'}
leaflet() %>% 
  addTiles() %>%
    setView(-93.65, 42.0285, zoom = 17) %>%
      addPopups(
    -93.65, 42.0285,
    'Here is the <b>Department of Statistics</b>, ISU')
```

## Map test 3

Below is a interactive map of the University of Canberra that shows the location of the statistics network [approx location currently].

```{r leaflet-map2, out.width='50%'}
leaflet() %>% 
  addTiles() %>%
    setView(-93.65, 42.0285, zoom = 17) %>%
      addPopups(
    -93.65, 42.0285,
    'Here is the <b>Department of Statistics</b>, ISU')
```

## Map test 4

Here is a collection of different themes.

```{r, echo=FALSE,message=FALSE, fig.height=4, fig.width=2, fig.show='hold'}
#devtools::install_github("wch/webshot")

library(leaflet)
library(htmltools)
library(RColorBrewer)

m1 <- leaflet(quakes) %>% 
        addTiles() %>% 
        addMarkers(lng=174.768, lat=-36.852)

m2 <- leaflet(quakes) %>% 
        addProviderTiles("Esri.WorldGrayCanvas") %>% 
        addMarkers(lng=174.768, lat=-36.852)

m3 <- leaflet(quakes) %>%
        addProviderTiles("Stamen.Toner") %>%
        addMarkers(lng=174.768, lat=-36.852)
m1
m2
m3
```

## Extracting mymaps data

This is for security reasons.

```{r}

```





