---
flexdashboard::flex_dashboard:
runtime: shiny
---
  
```{r libraries-info}
library(leaflet)
library(leaflet.extras)
```

# Resources

Using and applying GIS techniques in R has become much easier since the additional functionality of Java-script libraries. One of these libraries in the `leaflet` library for mapping. Below are some examples of these mapping tools with examples.

I like the idea of know what to do in arcGIS so that it is easy to work with researchers that use either R or arcGIS. For a GIS map there are two main options. Here are the resources for building interactive and static maps in R using a range of different packages:

- 'leaflet`

## Blogs

- A kol but outdated blog (sp not sf package); [Emily Burchfield](https://eburchfield.github.io/files/5_spatial_intro_lab.html)

## Extra resources

To begin with check this is working in your local RStudio enviroment

1. Install the required packages. You need a recent version of the GDAL, GEOS, Proj.4, and UDUNITS libraries installed for this to work on Mac and Linux. More information on that at https://github.com/r-spatial/sf#installling.

```{r}
# devtools::install_github("robinlovelace/geocompr")
```


2. Load the ones we need:

```{r}
library(spData)
library(dplyr)
library(sf)
library(bookdown)
library(leaflet)
library(leaflet.extras)
library(geojsonio)
```

3. Check it's all working, e.g. with this command:

```{r}
world %>%  plot()
```

And some blogging on the matter [here](http://zevross.com/blog/2014/09/30/use-the-amazing-d3-library-to-animate-a-path-on-a-leaflet-map/).

#### *Content below from leaflet github account*

## Using Basemaps

Leaflet supports basemaps using [map tiles](https://www.mapbox.com/guides/how-web-maps-work/), popularized by Google Maps and now used by nearly all interactive web maps.

### Default (OpenStreetMap) Tiles

The easiest way to add tiles is by calling `addTiles()` with no arguments; by default, [OpenStreetMap](https://www.openstreetmap.org/) tiles are used.

```{r fig.height=2.5}
m <- leaflet() %>% setView(lng = -71.0589, lat = 42.3601, zoom = 12)
m %>% addTiles()
```

### Third-Party Tiles

Alternatively, many popular free third-party basemaps can be added using the `addProviderTiles()` function, which is implemented using the [leaflet-providers plugin](https://github.com/leaflet-extras/leaflet-providers). See [here](http://leaflet-extras.github.io/leaflet-providers/preview/index.html) for the complete set.

As a convenience, leaflet also provides a named list of all the third-party tile providers that are supported by the plugin. This enables you to use auto-completion feature of your favorite R IDE (like RStudio) and not have to remember or look up supported tile providers; just type `providers$` and choose from one of the options. You can also use `names(providers)` to view all of the options.

```{r fig.height=1.25}
m %>% addProviderTiles(providers$Stamen.Toner)
m %>% addProviderTiles(providers$CartoDB.Positron)
m %>% addProviderTiles(providers$Esri.NatGeoWorldMap)
```

Note that some tile set providers require you to register; see the [project page](https://github.com/leaflet-extras/leaflet-providers) for more information. You can pass access tokens/keys, and other options, to the tile provider by populating the `options` argument with the `providerTileOptions()` function.

### Custom Tile URL Template

If you happen to have a custom map tile URL template to use, you can provide it as an argument to `addTiles()`.

### WMS Tiles

You can use `addWMSTiles()` to add WMS (Web Map Service) tiles. The map below shows the Base Reflectivity (a measure of the intensity of precipitation occurring) using the WMS from the [Iowa Environmental Mesonet ](http://mesonet.agron.iastate.edu):

```{r fig.height=2.5}
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 4) %>%
  addWMSTiles(
    "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
    layers = "nexrad-n0r-900913",
    options = WMSTileOptions(format = "image/png", transparent = TRUE),
    attribution = "Weather data © 2012 IEM Nexrad"
  )
```

### Combining Tile Layers

You aren't restricted to using a single basemap on a map; you can stack them by adding multiple tile layers. This generally only makes sense if the front tiles consist of semi transparent tiles, or have an adjusted opacity via the `options` argument.

```{r fig.height=1.75}
m %>% addProviderTiles(providers$MtbMap) %>%
  addProviderTiles(providers$Stamen.TonerLines,
    options = providerTileOptions(opacity = 0.35)) %>%
  addProviderTiles(providers$Stamen.TonerLabels)
```

## Choropleths

Making choropleths with leaflet is easy. In this example, we'll duplicate the [step-by-step choropleth tutorial](http://leafletjs.com/examples/choropleth/) from the Leaflet.js website.

The final result will look like this (scroll to the end to see the completed code):

```{r fig.height = 4.75, echo = FALSE}
# From http://leafletjs.com/examples/choropleth/us-states.js
# load necessary packages
library(geojsonio)
library(leaflet)

# transfrom .json file into a spatial polygons data frame
states <- 
    geojson_read( 
        x = "https://raw.githubusercontent.com/PublicaMundi/MappingAPI/master/data/geojson/us-states.json"
        , what = "sp"
    )

# check the class of the object
class( states )
# [1] "SpatialPolygonsDataFrame"
# attr(,"package")
# [1] "sp"

# end of script #

# Data Referenced from https://github.com/rstudio/leaflet/tree/master/docs/json/
# states <- geojsonio::geojson_read("./json/us-states.geojson", what = "sp")
bins <- c(0, 10, 20, 50, 100, 200, 500, 1000, Inf)
pal <- colorBin("YlOrRd", domain = states$density, bins = bins)
labels <- sprintf(
  "<strong>%s</strong><br/>%g people / mi<sup>2</sup>",
  states$name, states$density
) %>% lapply(htmltools::HTML)
leaflet(states) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(density),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
    position = "bottomright")
```

### Data source

We'll start by loading the data from JSON. While the Leaflet.js example loads the JSON directly into JavaScript, with the Leaflet R package we instead want to load the data into R.

In this case, we'll use the `geojsonio` package to load the data into `sp` objects, which will let us easily manipulate the geographic features, and their properties, in R.

```{r}
# states <- geojsonio::geojson_read("json/us-states.geojson", what = "sp")
class(states)
names(states)
```

As you can see, we now have a `SpatialPolygonsDataFrame` with `name` (state name) and `density` (population density in people/mi<sup>2</sup>) columns from the GeoJSON.

### Basic states map

Next, let's make a basic map with just the outline of the states. For our basemap, we'll use the same `"mapbox.light"` MapBox style that the example does; if you don't have a MapBox account, you can just use `addTiles()` in place of the `addProviderTiles` call, or choose a free provider.

```{r}
m <- leaflet(states) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
```

We've saved the basic basemap as a separate variable `m` so we can easily iterate on the `addPolygons` call as we work through the rest of the tutorial.

To add uniform polygons with default styling, just call `addPolygons` with no additional arguments.

```{r}
m %>% addPolygons()
```

### Adding some color

Now, let's color the states according to their population density. You have [various options](../colors.html) for mapping data to colors; for this example we'll match the Leaflet.js tutorial by mapping a specific set of bins into RColorBrewer colors.

First, we'll define the bins. This is a numeric vector that defines the boundaries between intervals (`(0,10]`, `(10,20]`, and so on).

Then, we'll call `colorBin` to generate a palette function that maps the RColorBrewer `"YlOrRd"` colors to our bins.

Finally, we'll modify `addPolygons` to use the palette function and the density values to generate a vector of colors for `fillColor`, and also add some other static style properties.

```{r}
bins <- c(0, 10, 20, 50, 100, 200, 500, 1000, Inf)
pal <- colorBin("YlOrRd", domain = states$density, bins = bins)
m %>% addPolygons(
  fillColor = ~pal(density),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7)
```

### Adding interaction

The next thing we'll want is to make the polygons highlight as the mouse passes over them. The `addPolygon` function has a `highlight` argument that makes this simple.

```{r}
m %>% addPolygons(
  fillColor = ~pal(density),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE))
```

(The Leaflet.js tutorial also adds an event handler that zooms into a state when it's clicked. This isn't currently possible with the Leaflet R package, except with either custom JavaScript or using Shiny, both of which are outside the scope of this example.)

### Custom info

Now let's expose the state names and values to the user.

The Leaflet.js tutorial shows the hovered-over state's information in a custom control. Again, that's possible by adding custom JavaScript or using Shiny, but for this example we'll use the built-in labels feature instead.

We'll generate the labels by handcrafting some HTML, and passing it to `lapply(htmltools::HTML)` so that Leaflet knows to treat each label as HTML instead of as plain text. We'll also set some label options to improve the style of the label element itself.

```{r}
labels <- sprintf(
  "<strong>%s</strong><br/>%g people / mi<sup>2</sup>",
  states$name, states$density
) %>% lapply(htmltools::HTML)
m <- m %>% addPolygons(
  fillColor = ~pal(density),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"))
m
```

This is the final version of our polygon layer, so let's save the result back to the `m` variable.

### Legend

As our final step, let's add a legend. Because we chose to color our map using `colorBin`, the `addLegend` function makes it particularly easy to add a legend with the correct colors and intervals.

```{r}
m %>% addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
  position = "bottomright")
```

## A single location on a map

Here is the birthplace of R plotted with `leaflet`, `addTiles` and the `addMarkers`...

```{r, echo = FALSE}
# my_data <- mpd.m
p_list <- list()

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
# m  
# save a ggplot

# Print the map

lm <- leaflet() %>% 
  addTiles() %>%
    setView(-93.65, 42.0285, zoom = 17) %>%
      addPopups(
    -93.65, 42.0285,
    'Here is the <b>Department of Statistics</b>, ISU')
# lm

p_list[[1]] <- list(print(m), "Map option 1")
p_list[[2]] <- list(print(lm), "Map option 2")
```

## Leaflet plots

*still coming*

## My Notes

I have sent the following colleagues to input into arcGIS and compare rendered maps/workflow issues with reproducibililty.

[*coming below*]

- Vignettes
  - Creating maps in R "www.ssnhub.com/creating-maps-in-r.html"
  - Map for Chapter 2: Beech forests ""

- Examples
  - LandCare 2019 publication here ""



